working title Compatibility system and stygma size of pollen recipient as main predictors of heterospecific pollen effect

### 2018-12-12 Manuscript_draft/Manuscript_draft.Rmd
some ideas

1.	 What are the implications of the findings?

>>>>

 What are the implications of the findings?

Ideas about pollen size in heterospecific pollen effect. (still have to develop it more...)

Let's classify pollen size in three groups in order to understand the interaction between pollen donor and recipient:
1) Donor pollen size < Recipient pollen size
2) Donor pollen size = Recipient pollen size
3) Donor pollen size > Recipient pollen size

1) Donor pollen size < Recipient pollen size

*Negative*

-Stigma clogging

-

### 2018-12-12 Manuscript_draft/Manuscript_draft.tex
some ideas

Let's classify pollen size in three groups in order to understand the
interaction between pollen donor and recipient. Donor's pollen: 1) Donor
pollen size \textless{} Recipient pollen size 2) Donor pollen size =
Recipient pollen size 3) Donor pollen size \textgreater{} Recipient
pollen size

>>>>

Let's classify pollen size in three groups in order to understand the
interaction between pollen donor and recipient: 1) Donor pollen size
\textless{} Recipient pollen size 2) Donor pollen size = Recipient
pollen size 3) Donor pollen size \textgreater{} Recipient pollen size
